---
title: "Untitled"
author: "Vincent"
date: "2021/10/31"
output: html_document
---
```{r}
 install.packages('curl')
# Observation by observation
concerts_obo <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = F)
# Feature by feature
concerts_fbf <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = T)
View(concerts_fbf)
```

```{r}
ex <- concerts_obo
```


Exercise 3.2 From concerts_obo,

Retrieve the 3rd and 5th concert observations and bind the result value with an object name concerts_sampled.

For the second concert, what are its first show’s time and location? Retrieve the information and bind the value with firstShowInfo.

```{r}
concerts_sampled <- concerts_obo[c(3,5)]

firstShowInfo <- concerts_obo[[2]][["showInfo"]][[1]][c("time","location")]
```



Exercise 3.3 From concerts_obo, due to Covid-19 the 3rd concert’s 1st show time is changed to “2022/01/31 19:30:00” and the location is changed to “Taichung Opera House”, please change the information

```{r}
concerts_obo[[3]][["showInfo"]][[1]][c("time","location")] <- list("time" = "2022/01/31 19:30:00","location" = "Taichung Opera House")
```

Exercise 3.4 How do you add the new born if you use JohnsFamilyCopy3$children[3] <-:


Copy
JohnsFamilyCopy3 <- JohnsFamily
JohnsFamilyCopy3$children[3] <-

```{r}
JohnsFamily <-
  list(
    name = "John", 
    age = 35,
    spouse = list(
      name = "Mary", 
      age = 32),
    children = list(
      list(
        name = "Bill", 
        age = 5),
      list(
        name = "Jane", 
        age = 3)
    )
  )
newborn <- list(
  list(
  name = "Lisa" ,
  age = 0
) )
JohnsFamilyCopy3 <- JohnsFamily
JohnsFamilyCopy3$children[3] <- newborn


```

Exercise 3.5 The 5th concert decides to add one more show which shares the same show information as its first show except the date is 2 days later.

```{r}
show2 <- concerts_obo[[5]][["showInfo"]][[1]]
concerts_obo[[5]][["showInfo"]][[2]] <- show2
concerts_obo[[5]][["showInfo"]][[2]][[1]] <-  "2021/12/27 19:30:00" 
```

Exercise 3.6 Due to Covid-19 concerts 2, 5, 7 are cancelled. Remove those three concerts from concerts_obo.

```{r}
concerts_obo <- concerts_obo[-c(2,5,7)]

```
